% resume.tex
%
% (c) 2002 Matthew Boedicker <mboedick@mboedick.org> (original author) http://mboedick.org
% (c) 2003 David J. Grant <dgrant@ieee.org> http://www.davidgrant.ca
% (c) 2007 Todd C. Miller <Todd.Miller@courtesan.com> http://www.courtesan.com/todd
% (c) 2009 Derek R. Hildreth <derek@derekhildreth.com> http://www.derekhildreth.com 
% (c) 2012 Reid Vandeweile <reidmv@gmail.com>
%This work is licensed under the Creative Commons Attribution-NonCommercial-ShareAlike License. To view a copy of this license, visit http://creativecommons.org/licenses/by-nc-sa/1.0/ or send a letter to Creative Commons, 559 Nathan Abbott Way, Stanford, California 94305, USA.

% GENERAL NOTE:  There may be some notes specific to myself.  If you're only interested in my LaTeX source or it doesn't make sense, please disregard it.

\documentclass[letterpaper,11pt]{article}
%-----------------------------------------------------------

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage[pdftex]{hyperref}
\hypersetup{
    colorlinks,%
    citecolor=black,%
    filecolor=black,%
    linkcolor=black,%
    urlcolor=mygreylink     % can put red here to visualize the links
}
\urlstyle{same}
\definecolor{mygrey}{gray}{.85}
\definecolor{mygreylink}{gray}{.30}
\textheight=9.0in
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{0.375in}
\addtolength{\textwidth}{0.5in}
\addtolength{\topmargin}{-.375in}
\addtolength{\textheight}{0.75in}
%-----------------------------------------------------------

%Custom commands

\newcommand{\resitem}[1]{
  \item #1 \vspace{-2pt}
}

\newcommand{\resheading}[1]{
  {
    \large \colorbox{mygrey}{
      \begin{minipage}{\textwidth}{
        \textbf{#1 \vphantom{p\^{E}}}
      }\end{minipage}
    }
  }
}

\newcommand{\ressubheading}[4]{
  \begin{tabular*}{6.75 in}{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{#3} & \textit{#4} \\
  \end{tabular*}\vspace{-6pt}
}

\newcommand{\mywebheader}{
  \begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}
    \textbf{\LARGE \textcolor{mygreylink}
      {Reid M Vandewiele}
    }
    & \href{mailto:reidmv@gmail.com}{reidmv@gmail.com}\\
    {\footnotesize \texttt
      {783 NW Naito Parkway \#530, Portland OR 97209}
    }
    & \textcolor{mygreylink}{{(503) 946-6126}}\\
  \end{tabular*}\\
  \vspace{0.1in}
}
%-----------------------------------------------------------

%-----------------------------------------------------------
%General Resume Tips
%   No periods!  Technically, nothing in this document is a full sentence.
%   Use parallelism by ending key words with the same thing,  i.e. "Coordinated; Designed; Communicated".
%   More tips on bottom of this LaTeX document.
%-----------------------------------------------------------

\begin{document}

% CHANGE HEADER SOURCE HERE
\mywebheader

%%%%%%%%%%%%%%%%%%%%%%
\resheading{Qualifications}
  \begin{description}
    \item[Puppet:] { \footnotesize
      Two years experience using and writing puppet code in a heterogeneous
      computing environment. Adapted a site's worth of pre-module practices to
      then-current practices, and continued to adapt codebase to reflect
      evolving best-practices. Developed and implemented the concept of 
      ``Dynamic Git-Branch Puppet Environments'' as popularized by Hunter
      Haugen while working at Portland State University.
    }
    \item[Learning:] { \footnotesize
      Strong personal belief that the ability to learn new skills, styles
      and methodologies is as important as the sum of a current skillset --
      this translates to a practiced ability to assimilate new ideas and a
      can-do attitude towards evolving workplace scenarios.
    }
    \item[Community:] { \footnotesize
      Community presence and engagement on {\sc irc} and on {\sc g}it{\sc h}ub using the
      handles ``reidmv'' and ``marut''. Contributions to the {\sc p}uppet community
      include published modules on the ``pdxcat'' {\sc g}it{\sc h}ub organization --
      providing custom types, providers, functions and application automation
      -- as well as patches and commentary submitted towards {\sc p}uppet {\sc l}abs
      published modules.
    }
    \item[Communication:] { \footnotesize
      Able to convey new ideas and concepts verbally and in writing using
      analogy, description and improvisation; engaging, listening and adapting
      as necessary to get the job done.
    }
  \end{description} % End Skills list
%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%
\resheading{Experience}
  \begin{description}
  
    \item
      \ressubheading{
        Portland State University Computer Action Team
      } {
        Portland, OR
      } {
        Lead Unix System Administrator
      } {
        Aug. 2010 -- Present
      } { \footnotesize
        \begin{itemize}
          \resitem{
            Managed a mixed paid/volunteer team of between 4-15 people
          }
          \resitem{
            Responsible for maintaining 200 workstations and servers running
            {\sc s}olaris, {\sc u}buntu, {\sc rhel}, {\sc c}ent{\sc os}, or
            {\sc n}exenta{\sc s}tor (primarily {\sc u}buntu)
          }
          \resitem{
            Provided and deployed a variety of infrastructure services
            and glue including: {\sc nfs}, autofs, amanda network backup, {\sc ldap}, ganeti,
            kvm, pam, apache, nginx, postgresql
          }
          \resitem{
            Built, found, evaluated and used {\sc p}uppet modules to automate system
            configuration across a heterogeneous environment
          }
          \resitem{
            Installed and managed a variety of simple and complex softwares for
            researchers and staff on-demand
          }
          \resitem{
            Maintained, extended, and on occasion rebuilt parts of a suite of
            in-house account management softwares written in perl, python, ruby,
            php, and various shell scripting languages
          }
        \end{itemize}
      }

    \item
      \ressubheading{
        Portland State University Computer Action Team
      } {
        Portland, OR
      } {
       ``TopDog'' Helpdesk Overseer
      } {
        Sep. 2009 -- Aug. 2010
      } { \footnotesize
        \begin{itemize}
          \resitem{
            Managed group of 40+ volunteers responsible for {\sc it} troubleshooting,
            customer-service and support
          }
          \resitem{
            Scheduled "braindump" training sessions and presentations for helpdesk
            volunteers
          }
          \resitem{
            Performed {\sc u}nix/{\sc l}inux system administration at a junior level
          }
        \end{itemize}
      }
      
    \item
      \ressubheading{
        Portland State University Computer Science Department
      } {
        Portland, OR
      } {
        Computer Science Tutor
      } {
        Apr. 2009 -- Aug. 2010
      } { \footnotesize
        \begin{itemize}
          \resitem{
            Tutored undergraduate computer science students in C++ and programming
            concepts (other languages used as necessary) focusing on entry-level
            through 300-level courses
          }
          \resitem{
            Promoted to {\sc t}utor {\sc c}oordinator in April 2010
          }
          \resitem{
            Hired, scheduled and managed a team of 4-6 student workers
          }
        \end{itemize}
      }
        
  \end{description} % End Experience list
%%%%%%%%%%%%%%%%%%%%%%
  
%%%%%%%%%%%%%%%%%%%%%%
\resheading{Education}
  \begin{description}
    \item
      \ressubheading{
        Portland State University
      } {
        Portland, OR
      } {
        \href{http://www.pdx.edu/computerscience}{Bachelor of Science in Computer Science}
      } {
        Sep. 2008 -- Aug. 2010
      }
    \item
      \ressubheading{
        Pacific University
      } {
        Forest Grove, OR
      } {
        \href{http://www.pacificu.edu/as/politics}{Bachelor of Arts in Politics \& Government}
      } {
        Aug. 2006 -- May. 2008
      }
    \item
      \ressubheading{
        Clackamas Community College
      } {
        Oregon City, OR
      } {
        \href{http://www.clackamas.edu/index.aspx}{AAOT General Studies}
      } {
        Jun. 2003 -- Jun. 2006
      }
  \end{description} % End Education list
%%%%%%%%%%%%%%%%%%%%%%

\end{document}
